%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy CV/Resume
% XeLaTeX Template
% Version 1.0 (5/5/2014)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Debarghya Das (http://www.debarghyadas.com)
% With extensive modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[letterpaper]{deedy-resume} % Use US Letter paper, change to a4paper for A4 
\usepackage{ragged2e}

\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------

\lastupdated % Print the Last Updated text at the top right

\namesection{Clayton}{Rayment}{ % Your name
\href{mailto:cw.rayment@gmail.com}{cw.rayment@gmail.com} | 970-402-3299 | \url{https://github.com/simharry3} % Your contact information
}

%----------------------------------------------------------------------------------------
%	LEFT COLUMN
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.33\textwidth} % The left column takes up 33% of the text width of the page
%------------------------------------------------
% Skills
%------------------------------------------------

\section{Skills}

\subsection{Programming}

\location{Fluent:}
C/C++ \textbullet{} Python \textbullet{} \LaTeX \textbullet{} Linux \\ 
\location{Familiar:}
IDL \textbullet{} MATLAB \textbullet{} Java \textbullet{} SQL\\
JS \textbullet{} LUA \textbullet{} Assembly \\
\location{Extensions:}
OpenCL \textbullet{} CUDA \textbullet{} OpenMP \textbullet{} MPI AstroPy
\vspace{5pt}\\

\subsection{Software}
\location{Astronomy}
MaxIM DL \textbullet{} Deep Sky Stacker\\
\location{CAD/CAM}
SolidWorks \textbullet{} Autodesk Inventor\\
\location{Misc}
Microsoft Office Suite

%------------------------------------------------
% Education
%------------------------------------------------

\section{Education} 

\subsection{Rensselaer Polytechnic}
\subsection{Institute}

\descript{MS in Computer Science\\}
\location{May 2018 | Troy, NY}
Department of Computer Science\\
\location{GPA: 3.34 / 4.0}

\descript{BS in Applied Physics\\}
\location{May, 2016 | Troy, NY}
Conc. in Computational Astrophysics \\
Department of Physics, Applied Physics,\\
and Astronomy\\
Dean's List (7/8 Semesters) \\
\location{GPA: 3.27 / 4.0}

%------------------------------------------------
% Coursework
%------------------------------------------------

\section{Coursework}

\subsection{Graduate}
Robotics I\\
Computer Operating Systems\\
Parallel Computing\\
Computer Graphics\\
Design and Analysis of Algorithms\\
Graph Theory\\~\\
%------------------------------------------------
\subsection{Undergraduate}
\descript{Computer Science:\\}
Data Structures\\
Programming in Java\\
Parallel Computing for Engineers\\
Foundations of Computer Science\\
Computer Organization\\
\descript{Physics:\\}
Quantum Physics I/II\\
Electromagnetic Theory\\
Theoretical Mechanics\\
Observational Astronomy\\
Astrophysics


%----------------------------------------------------------------------------------------

\end{minipage} % The end of the left column
\hfill
%
%----------------------------------------------------------------------------------------
%	RIGHT COLUMN
%----------------------------------------------------------------------------------------
%
\begin{minipage}[t]{0.66\textwidth} % The right column takes up 66% of the text width of the page
%------------------------------------------------
% Experience
%------------------------------------------------

\section{Experience}

\runsubsection{MilkyWay@Home}
\descript{| Researcher\\}
\location{Aug 2014 – Present | Troy, NY}
Work with Dr. Heidi Newberg on MilkyWay@Home, a distributed computing
project with a user base of over 20,000 active users, simulating dwarf galaxy tidal
stream formation. Research focused on parallelizing large-scale n-body calculations
to run on GPU compute devices using OpenCL.
\vspace{3pt}\\
% --------------------------------------------
\runsubsection{Hirsch Observatory}
\descript{| Operator\\}
\location{Jan 2016 – Present | Troy, NY}
Operator/Keyholder of the Hirsch Observatory. General responsibilities include operation of the 16" telescope, several smaller telescopes, and Observatory dome during public observing. Special responsibilities include CCD operation, data collection and reduction, and training members on CCD and telescope operation.
\vspace{3pt}\\
% --------------------------------------------
\runsubsection{Rensselaer Polytechnic Institute}
\descript{| Graduate TA\\}
\location{January 2017 – Present | Troy, NY}
Graduate Teaching Assistant for Stars, Galaxies, and the Cosmos, Intro to Astronomy and Astrophysics, and Observational Astronomy. Assisted with course
preparation and execution (Grading, proctoring, leading recitation, running night labs).
\vspace{3pt}\\
%------------------------------------------------
\runsubsection{AutoZone}
\descript{| Shift Manager\\}
\location{March 2016 - Aug 2016 | Troy, NY}
\vspace{3pt}
%------------------------------------------------
\runsubsection{Aims Community College}
\descript{| Robotics Instructor\\}
\location{Summer 2014, Summer 2015 | Longmont, CO}
Taught elementary through middle school students robotics using the LEGO
Mindstorms robotics platform. Used both NXT and EV3 kits, and facilitated a learning
environment appropriate for the age group.
\vspace{3pt}\\
% ------------------------------------------------
\runsubsection{Woodward Inc.}
\descript{| Engineering Intern\\}
\location{May 2013 - Aug 2013 | Fort Collins, CO}
\vspace{3pt}
%------------------------------------------------




%------------------------------------------------
% Extracurricular
%------------------------------------------------

\section{Extracurricular} 

\runsubsection{Rensselaer Sports Car Association}
\descript{| President\\}

\location{Aug 2014 – Aug 2016 | Troy, NY}
Presided over an institute-funded club which hosted autocross events and car meets
on campus. Managed several officers in the club, as well as oversaw event planning
and operation.
\vspace{3pt}\\

\runsubsection{Rensselaer Student Auto Shop}
\descript{| Manager\\}

\location{Aug 2014 – Dec 2017 | Troy, NY}
Managed shifts at a student-run on-campus auto shop. Helped customers diagnose,
repair, and prevent future problems. Frequent operation of heavy equipment such as a
10,000lb automotive lift, and machining tools. Large scale project
planning and execution was also common.


%------------------------------------------------
% Societies
%------------------------------------------------

\section{Projects}
\runsubsection{Amateur Astronomy}
Experience with several telescopes, tracking software, and imaging with DSLR, QSI 600, and SBIG 800 series CCDs. Used Python and IDL for astronomical data reduction, including quasar detection and asteroid tracking.\vspace{5pt}\\
\runsubsection{Competitive Robotics}~\\
\descript{VRC Team Captain} Captain of VRC team from 2008-2011. Qualified for, and attended World Championships during all three seasons. Recieved Build Award at World Championships for the 2011 season.\\
\descript{AVC Team Captain}Captain of team competing in SparkFun’s Autonomous Vehicle Challenge. Constructed 1/10 scale RC buggy capable of autonomous navigation using GPS, Compass, and tactile feedback.\vspace{5pt}\\

% \runsubsection{Automotive}~\\
% \descript{Race Engineering} Weight reduction, installation of safety equipment, including harnesses, roll bar, bucket seats, and fire mitigation. Multiple powertrain iterations completed, including individual throttle bodies, complete engine rebuild, and addition of forced induction. Fabrication of components including welding. Construction, programming, and installation of ECU, followed by tune optimization for peak performance and reliability.
%----------------------------------------------------------------------------------------

\end{minipage} % The end of the right column

\end{document}